---
title: "lab3b_2.2"
output: html_document
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
# long format
tablet = read_tsv("https://raw.githubusercontent.com/DATA2002/data/master/tablet1.txt")

# wide format
tabdat = gather(tablet, key = "lab", value = "measurement")

tabdat %>% 
  ggplot() + 
  aes(x = lab, y = measurement, fill = lab) + 
  geom_boxplot() + 
  theme_classic() + 
  labs(y = "Chlorpheniramine maleate (mg)",
       x = "Lab", fill = "")
```
*Figure 1: Boxplots of determinations of amounts of chlorpheniramine maleate in tablets by seven laboratories.*

**The boxplots in Figure 1 show some differences in the medians. Are these differences significant? We can address this by asking a variety of questions.**

## Question 1. 
**Is the mean level of chlorpheniramine maleate in tablets from Lab 1 different from 4.0? State the null hypothesis.**

We use a one sample t-test.
$H_0: \mu_i=4$ vs. $H_1:\mu_1\neq4$
```{r}
t.test(tablet$Lab1, mu = 4)
```
Therefore, the mean level in Lab 1 is different to 4.

## Question 2.
**Is the mean level of chlorpheniramine maleate in tablets from Lab 1 different from that from Lab 3?**

Here we use a two sample t-test.
$H_0:\mu_1=u_3$ vs. $H_1:\mu_1\neq \mu_3$
```{r}
t.test(tablet$Lab1, tablet$Lab3)
```
Here we can see that the means of Lab1 and Lab3 results are different. 

## Question 3.
**Perform a one-way ANOVA to test if the mean levels of chlorpheniramine maleate differ across the seven labs.**

```{r}
lab_anova = aov(measurement ~ lab, data = tabdat)
summary(lab_anova)
```
$F = 5.66\mbox{, df}=6,63\mbox{, }p<0.0001$

Here we can see that the p-value is << 0.05 therefore, we can conclude that there must be at least 2 groups that differ in means.

## Question 4.
**Obtain a QQ plot of the residuals and comment on the validity of the ANOVA assumptions.**

```{r, warning = FALSE, message = FALSE, echo = FALSE}
library(ggfortify)
autoplot(lab_anova, which = c(1,2)) + theme_classic()
```

On the left plot we can see that the blue line isn't close to 0 therefore, the middle groups don't have much equal variance.

And on the right plot we can assume normality because most of the points lie on the QQ line, however, there are a few towards the low end that deviates from this line. Furthermore, we can rely on the central limit theorem to ensure our inferences are valid.


## Question 5.
**Perform pairwise post hoc tests to determine which labs are significantly different.**

To do this we can once again use the emmeans package.

```{r, warning = FALSE, message = FALSE, echo = FALSE}
library(emmeans)
lab_em = emmeans(lab_anova, ~ lab)
lab_pair = contrast(lab_em, method = "pairwise", adjust = "bonferroni")
# lab_pair

# filter out all lab pairs which have a p.value of less than 0.1 and tabulate
lab_pair %>%
  data.frame() %>% 
  filter(p.value < 0.05) %>% 
  knitr::kable(digits = 4)
```
Here we have filtered out all the significant contrasts and tabulated them above. Furthermore, all the pairwise mean differences are plotted.
```{r, echo = FALSE}
plot(lab_pair) + theme_bw() +
  labs(x = "Pairwise mean difference") + 
  geom_vline(xintercept = 0)
```
We can conclude that Lab1 is significantly different to Labs 4,5 and 6.

## Question 6.
**Use a rank based approach to testing for a difference between the means of the 7 labs.**

```{r}
kruskal.test(measurement ~ factor(lab), data = tabdat)
```
$\chi^2=29.6 \mbox{, df}=6\mbox{, }p<0.001$

Therefore, the Kruskal-Wallis test shows that there is significance difference between the means of the 7 labs.
