---
title: "lab3a_3.3"
output: html_document
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(sgof)
library(tidyverse)
```

## (a)
**How many p-values are in the data set?**

```{r, echo = FALSE}
nrow(Hedenfalk)
```
Each entry in this data frame is a p-value.

## (b)
**Generate a histogram of the (unadjusted) Hedenfalk p-values.**

```{r, warning = FALSE, echo = FALSE}
ggplot(Hedenfalk, aes(x = x)) + geom_histogram(boundary = 0, binwidth = 0.05) + 
  labs(x = "Unadjusted p-value", y = "Count") + theme_bw()
```

## (c)
**How many (unadjusted) p-values are significant at the 5% level of significance? What proportion of all p-values in the data set is this?**

```{r, echo = FALSE}
num_significant = sum(Hedenfalk$x < 0.05)
proportion = num_significant/nrow(Hedenfalk)
proportion
# or we can use the mean
# mean(Hedenfalk$x < 0.05)
```
## (d)
**Why is it a good idea to consider adjusted p-values?**

By chance alone we should see $3170 \times 0.05=158.8$ false positives however, here we have 605 false positives therefore, to make sure our result is correct, it is a good idea to consider adjustments because the FWER grows as the number of comparisons get larger.

## (e)
**Using p.adjust() find the Bonferroni and BH p-values. Plot histograms of each and find the number of significant results after adjustment for both.**

```{r, warning = FALSE, echo = FALSE}
Hedenfalk = Hedenfalk %>% 
  mutate(
    bonf_p = p.adjust(x, method = "bonferroni"),
    BH_p = p.adjust(x, method = "BH")
)

# log transformation performed because the scaling was bad
p1 = ggplot(Hedenfalk, aes(x = bonf_p)) + 
  geom_histogram(boundary = 0, binwidth = 0.05) +
  theme_bw() + 
  labs(x = "bonferroni adjusted p-value", y = "Count") +
  scale_y_log10()

p2 = ggplot(Hedenfalk, aes(BH_p)) +
  geom_histogram(boundary = 0, binwidth = 0.05) +
  theme_bw()

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

Number of significant p-values and proportion for the Bonferroni method
```{r, echo = FALSE}
# number of significant for bonferroni
sum(Hedenfalk$bonf_p < 0.05)
mean(Hedenfalk$bonf_p < 0.05) # proportion
```


Number of significant p-values and proportion for the BH method
```{r, echo = FALSE}
# number of significant for BH
sum(Hedenfalk$BH_p < 0.05)
mean(Hedenfalk$BH_p < 0.05) # proportion
```

## (f)
**Comment on the difference between the Bonferroni method and the BH method.**

Bonferroni method is more conservative and controls the FWER whereas the BH method allows for more false positives and controls the FDR.




